\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-12-15 appendix-1.Rmd
Cross references are checked

---
title             : "Supplementary"
shorttitle        : "SA"

author: 
  - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "1, *"
    email         : "mushfiqul.anwarsiraji@monash.edu"
    role:         
      - Formal Analysis
      - Visualization
      - Writing – original draft
      - Writing – review & editing;

  - name          : "Rafael Robert Lazar"
    affiliation   : "2, 3, *"
    role:
      - Data curation
      - Investigation
      - Project administration
      - Visualization
      - Writing – original draft
      - Writing – review & editing;

  - name          : "Juliëtte	van Duijnhoven"
    affiliation   : "4"
    email         : "j.v.duijnhoven1@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

  - name          : "Luc Schlangen"
    affiliation   : "5"
    email         : "l.j.m.schlangen@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

  - name          : "Shamsul Haque"
    affiliation   : "1"
    email         : "shamsul@monash.edu"
    role:         
      - Conceptualization
      - Supervision
      - Writing – review & editing

  - name          : "Vineetha Kalavally"
    affiliation   : "6"
    email         : "vineetha@monash.edu"
    role:         
      - Supervision
      - Writing – review & editing

  - name          : "Céline Vetter"
    affiliation   : "7, 8"
    email         : "celine.vetter@colorado.edu"
    role:         
      - Conceptualization
      - Writing – review & editing

  - name          : "Gena Glickman"
    affiliation   : "9"
    email         : "gena.glickman@usuhs.edu"
    role:         
      - Conceptualization
      - Methodology
      - Writing – review & editing

  - name          : "Karin Smolders"
    affiliation   : "10"
    email         : "k.c.h.j.smolders@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Writing – review & editing

  - name          : "Manuel Spitschan"
    corresponding : yes
    affiliation   : "11, 2, 3"
    email         : "manuel.spitschan@psy.ox.ac.uk"
    role:         
      - Conceptualization
      - Data curation
      - Investigation
      - Project administration
      - Visualization
      - Methodology
      - Writing – original draft
      - Writing – review & editing

affiliation:
  - id            : "1"
    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
  - id            : "2"
    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
  - id            : "3"
    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
  - id            : "4"
    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
  - id            : "5"
    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands"
  - id            : "6"
    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia"
  - id            : "7"
    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
  - id            : "8"
    institution   : "Ximes GmbH, Frankfurt, Germany"
  - id            : "9"
    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
  - id            : "10"
    institution   : "Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands"
  - id            : "11"
    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, UK"
  - id            : "*"
    institution   : "Joint first author"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    latex_engine: xelatex
    includes:
      in_header: header.tex

mainfont: Arial
---

```{r options, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
set.seed(123)
par(family = "Arial")
```

@@

# SA: Confirming the five factor solution obtained using minimum residual extraction method

@@

# SA: Factor analysis with six factors

@@

# SA: Factor Analysis with Unmerged Response Option

@@

Table \@ref(tab:tabDesAppB) summarizes the univariate descriptive statistics for the 48 items with un-merged options. Some of the items were skewed with high Kurtosis values. Our data violated both univariate normality (Shapiro-Wilk statistics) and multivariate normality assumptions [Marida's test]. Multivariate skew was = `r printnum(mardia.1$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia.1$b2p)` (p <0.001). Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen. Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy. The overall KMO vale for 48 items was `r printnum(KMO.1$MSA)` which was above the cutoff value (.50) indicating a mediocre sample. Bartlett's test of sphericity, $\chi^2$ (`r bartlet.1$df`) = `r apa(bartlet.1$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for the EFA. However only `r apa(cor.per.1, 2,T)`% of the inter-item correlation coefficients were greater than .30. The absolute value of inter-item correlation ranged between `r min.cor.1` to `r max.cor.1`.Figure \@ref(fig:figCorAppB) depicts the correlation matrix. For un-merged response option Horn's parallel analysis with 500 iterations indicated a five-factor solution. However, Scree plot and the MAP method suggested 6-factor solution. five-factor solution . As a result, we tested both five-factor and six-factor solutions. The six factor solution yielded a factor with only two salient loading (Table \@ref(tab:EFAsix). Thus we reject the six factor solution. The five factor solution retained 24 items (Table \@ref(tab:EFATableAppB)). However the factors are less interpretable in terms of common theme. Thus we reject the five factor solution.

@@

```{r figCorAppB, fig.cap="Correlation plot of the items [Unmerged response options]", include=FALSE, out.width="100%"}

@@

```{r EFATableAppB, results='asis'}
apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
```

@@

# Geographic Locations of Survey Participants
```{r TzTable, include=FALSE, warning=F,message=FALSE}
descriptives.data%>%
  tbl_summary(
    label = slypos_demographics_tz.factor ~ "Time zone - Country",
    statistic = list(all_categorical() ~ "{n} ({p}%)"),
    missing = "no",
    sort = all_categorical() ~ "frequency",
    include = "slypos_demographics_tz.factor"
  )  %>% bold_labels() %>% 
  modify_header(label ~ "") %>%
  modify_caption("Geographical Location") -> tz_table

@@

```{r tzTabPrint, results='asis'}

>>>>

```{r options-appendix, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
set.seed(123)
par(family = "Arial")
```

@@

```{r F1IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F1testinfo.png')
```

```{r F2IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F2testinfo.png')
```

```{r F3IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F3testinfo.png')
```

```{r F4IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F4testinfo.png')
```

```{r F5IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F5testinfo.png')
```

# Confirming the five factor solution obtained using minimum residual extraction method

@@

# Factor analysis with six factors

@@

# Factor Analysis with Unmerged Response Option

@@

Table \@ref(tab:tabDesAppB) summarizes the univariate descriptive statistics for the 48 items with un-merged options. Some of the items were skewed with high Kurtosis values. Our data violated both univariate normality (Shapiro-Wilk statistics) and multivariate normality assumptions [Marida's test]. Multivariate skew was = `r printnum(mardia.1$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia.1$b2p)` (p <0.001). Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen. Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy. The overall KMO vale for 48 items was `r printnum(KMO.1$MSA)` which was above the cutoff value (.50) indicating a mediocre sample. Bartlett's test of sphericity, $\chi^2$ (`r bartlet.1$df`) = `r apa(bartlet.1$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for the EFA. However only `r apa(cor.per.1, 2,T)`% of the inter-item correlation coefficients were greater than .30. The absolute value of inter-item correlation ranged between `r min.cor.1` to `r max.cor.1`.Figure \@ref(fig:corunm) depicts the correlation matrix. For un-merged response option Horn's parallel analysis with 500 iterations indicated a five-factor solution. However, Scree plot and the MAP method suggested 6-factor solution. five-factor solution . As a result, we tested both five-factor and six-factor solutions. The six factor solution yielded a factor with only two salient loading (Table \@ref(tab:EFAsix). Thus we reject the six factor solution. The five factor solution retained 24 items (Table \@ref(tab:efaunmerged)). However the factors are less interpretable in terms of common theme. Thus we reject the five factor solution.

@@

```{r corunm, fig.cap="Correlation plot of the items [Unmerged response options]",  out.width="100%"}

@@

```{r efaunmerged, results='asis'}
apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
```

@@

# Geographic Locations of Survey Participants
```{r Timezone-tab, include=FALSE, warning=F,message=FALSE}
descriptives.data%>%
  tbl_summary(
    label = slypos_demographics_tz.factor ~ "Time zone - Country",
    statistic = list(all_categorical() ~ "{n} ({p}%)"),
    missing = "no",
    sort = all_categorical() ~ "frequency",
    include = "slypos_demographics_tz.factor"
  )  %>% bold_labels() %>% 
  modify_header(label ~ "") %>%
  modify_caption("Geographical Location") -> tz_table

@@

```{r tztabprint, results='asis'}

### 2021-12-15 manuscript.Rmd
Cross references are checked

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

@@

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    latex_engine: xelatex
    includes:
      in_header: header.tex
appendix:
  - "Supplymentary.Rmd"
  - "instrument.Rmd"
mainfont: Arial
---

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200)
options(knitr.duplicate.label = "allow")
set.seed(123)
par(family = "Arial")
```

@@

```{r scalePrint, results='asis'}
relevant.scale.data %>%
   kable( booktabs = T, caption ="Releated Scales", format ="latex", longtable =T) %>% 
  kable_styling(latex_options = c("repeat_header")) %>% 
  column_spec(1:6, width = "2cm")
```

@@

Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis. In our analysis we used R (version 4.1.0), with several R packages. Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always). Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we decided to collapse them into one, making it a 5 point Likert type response format. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used  polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA. We employed principal axis (PA) as  factor extraction method with varimax rotation. PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020]. The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well. We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. Additionally, to determine the simple structure, we followed the guidelines recommended by psychometricians: (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018]. We confirmed the latent structure obtained in the EFA by conducting a categorical "Confirmatory Factor Analysis" (CFA) using "robust weighted least square estimator" (WLSMV). We estiablished the measurement invariance of our tool across the native and non-native English speakers using structural equation model framework. To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic]. Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
We also conducted psychometric analysis on non-merged response options data (Supp. Table \@ref(tab:EFATableAppB)) and rejected the latent structure obtained as the factors were less interpretable.

@@

parallel = ggplot(Adjusted.EV, aes(x=num, y=eigenvalue, shape=type, color=type)) +
  #Add lines connecting data points
  geom_line()+
    #geom_line(data = Random.EV) +
  #geom_line(data = Unadjusted.EV)+
    #Add the data points.
  geom_point(size=3)+
  #geom_point(data = Random.EV, size=3)+
  #geom_point(data = Unadjusted.EV, size=3)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 7), breaks=seq(0,7,1)) +
   #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
  scale_x_continuous(name='Factor Number (Parallel Analysis)', limits=c(0, 48),breaks=seq(0,48,4))+
    #Add vertical line indicating parallel analysis suggested max # of factors to retain
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(text = element_text(size = 25),legend.position = "None")

@@

scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
   geom_line()+
  #geom_line(data = PA.Scree)+ 
  geom_point(size=3)+
  #geom_point(data = PA.Scree, size=3)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
  scale_x_continuous(name='Factor Number (Scree Plot)', limits=c(0, 20),breaks=seq(0,20,4))+
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(text = element_text(size = 25),legend.position = "None")

@@

```{r HullEFA, include=FALSE}
# HULL
EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL) +xlab("Factor Number (Hull Method)")+ylab("CAF")+ 
  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2"))+theme(text = element_text(size = 25))  
```

@@

```{r facIdFig, out.height="250%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")

@@

## Developing Short form of LEBA
We sought the item response theory (IRT) to develop the short form of LEBA. IRT the conventional classical test theory-based analysis by gathering information on item quality by indices like item difficulty,item discrimination, and item information[@bakerBasicsItemResponse2017]. IRT judges the item's quality on item information in relation to participants' latent trait level ($\theta$). We gathered evidence on item quality by fitting each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA. @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70. Table \@ref(tab:IRTparameters) summarizes the IRT parameters of our tool. Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$). Examination of the item information curve \@ref(fig:itmeinfo) indicated 5 items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20) thus discarded creating a short form of LEBA with 5 factors and 18 items.

@@

```{r saveiteminfo, include=FALSE}
jpeg("Manuscript.figures/iteminfo.png", width = 800, height = 750)
plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = "AUTO", label_size = 10,align = "v",ncol = 2)

@@

@@

```{r itmeinfo, fig.cap="Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="60%"}
knitr::include_graphics('Manuscript.figures/iteminfo.png')

@@

```{r, warning=F, include=FALSE}
library(WrightMap)
library(RColorBrewer)
F1.e <- as.data.frame(F1.estimation)
F2.e <- as.data.frame(F2.estimation)
F3.e <- as.data.frame(F3.estimation)
F4.e <- as.data.frame(F4.estimation)
F5.e <- as.data.frame(F5.estimation)

@@

```{r WP, fig.cap="Person Item Map (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
library(WrightMap)
wrightMap(estimation, threshold, 
          item.prop = 0.65,

          main.title = "LEBA",
          dim.names = c("F1", "F2", "F3", "F4", "F5"),
          thr.sym.col.fg = itemlevelcolors,
          thr.sym.col.bg = itemlevelcolors,
          vertLines = TRUE,
          show.thr.lab = T,
          dim.color = brewer.pal(5, "Set3"))

@@

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('Supplymentary.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('instrument.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('Supplymentary.Rmd')
```

```{r echo = FALSE, results = 'asis', cache = FALSE}
papaja::render_appendix('instrument.Rmd')
```

>>>>

authornote: |
  This research is supported by funding from the Welcome Trust (204686/Z/16/Z), the European Training Network LIGHTCAP (project number 860613) under the Marie Skłodowska-Curie actions framework H2020-MSCA-ITN-2019, the BioClock project (number 1292.19.077) of the research program Dutch Research Agenda: Onderzoek op Routes door Consortia (NWA-ORC) which is (partly) financed by the Dutch Research Council (NWO), and the European Union and the nationals contributing in the context of the ECSEL Joint Undertaking programme (2021-2024) under the grant #101007319.

@@

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    latex_engine: xelatex
    includes:
      in_header: header.tex
appendix:
  - "appendix-1.Rmd"
  - "appendix-2.Rmd"
mainfont: Arial
---

```{r setup, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200)
#options(knitr.duplicate.label = "allow")
set.seed(123)
par(family = "Arial")
```

@@

```{r scale-print, results='asis'}
relevant.scale.data %>%
   kable( booktabs = T, caption ="Releated Scales", format ="latex", longtable =T) %>% 
  kable_styling(latex_options = c("repeat_header")) %>% 
  column_spec(1:6, width = "2cm")
```

@@

Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis. In our analysis we used R (version 4.1.0), with several R packages. Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always). Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we decided to collapse them into one, making it a 5 point Likert type response format. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used  polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA. We employed principal axis (PA) as  factor extraction method with varimax rotation. PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020]. The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well. We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. Additionally, to determine the simple structure, we followed the guidelines recommended by psychometricians: (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018]. We confirmed the latent structure obtained in the EFA by conducting a categorical "Confirmatory Factor Analysis" (CFA) using "robust weighted least square estimator" (WLSMV). We estiablished the measurement invariance of our tool across the native and non-native English speakers using structural equation model framework. To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic]. Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
We also conducted psychometric analysis on non-merged response options data (Supp. Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.

@@

parallel = ggplot(Adjusted.EV, aes(x=num, y=eigenvalue, shape=type, color=type)) +
  #Add lines connecting data points
  geom_line()+
    #geom_line(data = Random.EV) +
  #geom_line(data = Unadjusted.EV)+
    #Add the data points.
  geom_point(size=1)+
  #geom_point(data = Random.EV, size=3)+
  #geom_point(data = Unadjusted.EV, size=3)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 7), breaks=seq(0,7,1)) +
   #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
  scale_x_continuous(name='Factor Number (Parallel Analysis)', limits=c(0, 48),breaks=seq(0,48,4))+
    #Add vertical line indicating parallel analysis suggested max # of factors to retain
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(,legend.position = "None") 
#text = element_text(size = 25)

@@

scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
   geom_line()+
  #geom_line(data = PA.Scree)+ 
  geom_point(size=1)+
  #geom_point(data = PA.Scree, size=3)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
  scale_x_continuous(name='Factor Number (Scree Plot)', limits=c(0, 20),breaks=seq(0,20,4))+
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(legend.position = "None") 
#text = element_text(size = 25

@@

```{r HullEFA, include=FALSE}
# HULL
EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL) +xlab("Factor Number (Hull Method)")+ylab("CAF")+ 
  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2"))+theme(legend.position = "None") 
```

@@

```{r facIdFig, out.height="350%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")

@@

## Developing Short form of LEBA
We sought the item response theory (IRT) to develop the short form of LEBA. IRT the conventional classical test theory-based analysis by gathering information on item quality by indices like item difficulty,item discrimination, and item information[@bakerBasicsItemResponse2017]. IRT judges the item's quality on item information in relation to participants' latent trait level ($\theta$). We gathered evidence on item quality by fitting each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA. @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70. Table \@ref(tab:IRTparameters) summarizes the IRT parameters of our tool. Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$). Examination of the item information curve (Sup.fig \@ref(fig:F2IF)-\@ref(fig:F5IF)) indicated 5 items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20) thus discarded creating a short form of LEBA with 5 factors and 18 items.

@@

```{r saveiteminfo, eval=FALSE, include=FALSE}
jpeg("Manuscript.figures/iteminfo.png", width = 800, height = 750)
plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
          labels = "AUTO", label_size = 10,align = "v",ncol = 2)

@@

```{r iteminfo, include=F, warning=F}
F1_item1<- plot(F1_fit, type = "infotrace", 
                    facet_items = T, which.items = 1, main = "")

F1_item2 <- plot(F1_fit, type = "infotrace", 
     facet_items = T, which.items = 2,main = "")

F1_item3 <- plot(F1_fit, type = "infotrace", 
     facet_items = T, which.items = 3,main = "")

F2_item1 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 1,main = "")
F2_item2 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 2,main = "")
F2_item3 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 3,main = "")
F2_item4 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 4,main = "")
F2_item5 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 5,main = "")
F2_item6 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 6,main = "")

F3_item1 <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, which.items = 1,main = "")
F3_item2 <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, which.items = 2,main = "")

F3_item3 <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, which.items = 3,main = "")
F3_item4 <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, which.items = 4,main = "")
F3_item5 <- plot(F3_fit, type = "infotrace", 
                    facet_items = T, which.items = 5,main = "")

F4_item1 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 1,main = "")
F4_item2 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 2,main = "")
F4_item3 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 3,main = "")
F4_item4 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 4,main = "")

F5_item1 <- plot(F5_fit, type = "infotrace", facet_items = T,which.items = 1,main = "")
F5_item2 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 2,main = "")
F5_item3 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 3,main = "")
F5_item4 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 4,main = "")
F5_item5 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 5,main = "")

F1title <- ggdraw() + 
  draw_label(
    "F1: Wearing blue light filters",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )

F2title <- ggdraw() + 
  draw_label(
    "F2: Spending time outdoors",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )

F3title <- ggdraw() + 
  draw_label(
    "F3: Using phone and smart-watch in bed",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )

F4title <- ggdraw() + 
  draw_label(
    "F4: Using light before bedtime",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )

F5title <- ggdraw() + 
  draw_label(
    "F5: Using light...daytime",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )

f1itemplot <- plot_grid(F1_item1, F1_item2,F1_item3,
          labels = "AUTO", label_size = 10,align = "v")
f2itemplot <- plot_grid(F2_item1, F2_item2,F2_item3,F2_item4,F2_item5,F2_item6,
           label_size = 10,align = "v")
f3itemplot <- plot_grid(F3_item1, F3_item2,F3_item3,F3_item4,F3_item5,
           label_size = 10,align = "v")
f4itemplot <- plot_grid(F4_item1, F4_item2,F4_item3,F4_item4,
          labels = "AUTO", label_size = 10,align = "v")

f5itemplot <- plot_grid(F5_item1, F5_item2,F5_item3,F5_item4,F5_item5,
          label_size = 10,align = "v")
```

```{r f1itminf, include=F, warning=F}

jpeg("Manuscript.figures/F1testinfo.png", width = 800, height = 750)

plot_grid(
  F1title, f1itemplot,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)

)
dev.off()
```

```{r f2iteminf, include=F, warning=F}
jpeg("Manuscript.figures/F2testinfo.png", width = 800, height = 750)
plot_grid(
  F2title, f2itemplot,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)
)
dev.off()
```

```{r f3iteminf, include=F, warning=F}
jpeg("Manuscript.figures/F3testinfo.png", width = 800, height = 750)
plot_grid(
  F3title, f3itemplot,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)
)
dev.off()
```

```{r f4iteminf, include=F, warning=F}
jpeg("Manuscript.figures/F4testinfo.png", width = 800, height = 750)
plot_grid(
  F4title, f4itemplot,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)
)
dev.off()
```

```{r f5iteminf, include=F, warning=F}
jpeg("Manuscript.figures/F5testinfo.png", width = 800, height = 750)
plot_grid(
  F5title, f5itemplot,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)
)
dev.off()
```

@@

```{r itmeinfo, eval=FALSE, fig.cap="Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, include=FALSE, out.height="60%", out.width="100%"}
knitr::include_graphics('Manuscript.figures/iteminfo.png')

@@

```{r WPdata, warning=F, include=FALSE}

library(RColorBrewer)
F1.e <- as.data.frame(F1.estimation)
F2.e <- as.data.frame(F2.estimation)
F3.e <- as.data.frame(F3.estimation)
F4.e <- as.data.frame(F4.estimation)
F5.e <- as.data.frame(F5.estimation)

@@

```{r saveWrightmao, include=FALSE, warning=F, message=F}
jpeg("Manuscript.figures/wm.png", width = 800, height = 750)
WrightMap::wrightMap(estimation, threshold, 
          item.prop = 0.65,

          main.title = "LEBA",
          dim.names = c("F1", "F2", "F3", "F4", "F5"),
          thr.sym.col.fg = itemlevelcolors,
          thr.sym.col.bg = itemlevelcolors,
          vertLines = TRUE,
          show.thr.lab = T,
          dim.color = brewer.pal(5, "Set3"))
dev.off()
```

```{r WP, fig.cap="Person Item Map", warning=FALSE, out.width="100%", out.height="120%"}

knitr::include_graphics('Manuscript.figures/wm.png')
```

@@
